ODGI: understanding pangenome graphs

### 2021-11-09 manuscript/main.tex
lingering parentheses

Pangenome graphs can be constructed by multiple sequence alignment~\citep{Lee_2002,Grasso_2004} or by transitively reducing an alignment between sequences to an equivalent, labeled sequence graph~\citep{Kehr_2014,Garrison_2019_thesis}.
Current methods to build these graphs are still under active development~\citep{Li:2020,Armstrong:2020,pggb}, but they have largely settled on a common data model, represented in the Graphical Fragment Assembly (GFA) format~\citep{GFA}).
%\FIXME{may want to move GFA standard+VG to intro section 1}. AG: it is borderline, but it seems fine to have it here too.
This standardization supports the development of a reference set of tools that operate on the pangenome graph model.
Such an effort began with the VG toolkit~\citep{Garrison:2018}.
Here we refocus it with ODGI, a compatible, but independent set of algorithms focused on visualization, interrogation, and transformation of pangenome graphs.

>>>>

Pangenome graphs can be constructed by multiple sequence alignment~\citep{Lee_2002,Grasso_2004} or by transitively reducing an alignment between sequences to an equivalent, labeled sequence graph~\citep{Kehr_2014,Garrison_2019_thesis}.
Current methods to build these graphs are still under active development~\citep{Li:2020,Armstrong:2020,pggb}, but they have largely settled on a common data model, represented in the Graphical Fragment Assembly (GFA) format~\citep{GFA}.
%\FIXME{may want to move GFA standard+VG to intro section 1}. AG: it is borderline, but it seems fine to have it here too.
This standardization supports the development of a reference set of tools that operate on the pangenome graph model.
Such an effort began with the VG toolkit~\citep{Garrison:2018}.
Here we refocus it with ODGI, a compatible, but independent set of algorithms focused on visualization, interrogation, and transformation of pangenome graphs.
